---
editor: 
  markdown: 
    wrap: sentence
---

```{r, echo = FALSE, message = FALSE, include = FALSE}
source(here::here("Script/Regression.R"))
```

# Regression

## Correlations

To see how our data may be correlated, we will start by running a correlation analysis.

```{r, echo = FALSE, message = FALSE}
knitr::kable(corr_matrix, format = "html")
```

```{r, echo = FALSE, message = FALSE, results='asis'}
corplot
```

We first decide to compute the correlations with all of our variables dividing « crimes » in every crime categories to see if there are interesting correlation links to explain them.
As we can see **Burglaries** are highly correlated with Immigration rate and Unemployment rate and negatively correlated to the No diploma rate.
On the other side **Assault and Battery** is mainly correlated to poverty rate and No Diploma rate.
**Intentional Damage** behave the same as **Assault and Battery**, it is also interesting to observe that voting for Marin Lepen is positively correlated with these two variables.
For **Drug use** we observe that the two more correlated variables are Immigration and Unemployment rate.
And finally we observe that **Theft without violence** only has small correlations with all of our explicative variables.

## Linear regression

We started by scaling all variables, expressing them in percentages except for density (people/km\^2) and Win_Lepen (a binary variable ranging from 0 to 1).
The initial regression included the average of all crimes and potential explanatory variables.
Subsequently, we conducted a stepwise regression AIC test to identify indispensable variables, leading to the removal of Win_Lepen, Intensity Poverty, Poverty, and No Diploma Rate.

### All crimes

The initial regression includes the average of all crimes and potential explanatory variables.
With a formula as seen below:

$RatePer1k = \beta_0 + \beta_1 Density + \beta_2WinLepen + \beta_3Poverty + \beta_4NoDiplomaRate + \beta_5ImmigrationRate + \beta_5UnemploymentRate + \beta_6IntensityPoverty + \beta_6 Total Pop$

Subsequently, we conducted a stepwise regression AIC test to identify indispensable variables, leading to the removal of Win_Lepen, Intensity Poverty, Poverty, and No Diploma Rate.

```{r, results='asis'}
step(Assault_model_full, scope = list(lower= Assault_model_null, upper=Assault_model_full),
     direction = "backward")
```

We find this reduced model.
compared to our full model

```{r, echo = FALSE, message = FALSE, results='asis'}
x <- Full_model %>% 
  tbl_regression()
y <- Reduce_model %>% 
  tbl_regression()

tbl_merge(
  tbls = list(x, y),
  tab_spanner = c("**Full model**", "**Reduced model**")
)
```

VIF analysis for our reduced model

```{r, echo = FALSE, message = FALSE}
knitr::kable(t(as.data.frame(vif(Reduce_model))), format = "html")
```

The remaining significant variables, including Immigration, Unemployment, TotalPop, and Density, passed the Variance Inflation Factor test, ensuring no issues of multicollinearity (VIF score \< 5).
However, we noted a low Adjusted R-Squared, indicating that our model explained only a small proportion of the data.
To address this, we performed separate regressions for the five most prevalent crime categories in France: Assault and Battery, Burglaries, Wilful Damage and Destructions, Drug Use, and Theft without Violence.

It's crucial to emphasize that the stepwise regression with AIC mentioned earlier was applied to each of our regressions.
The regressions presented below have been refined to exclude irrelevant variables based on this test.

### Assault and Battery

We run a stepwise regression with Asssault and Battery as the dependent variable

```{r, echo = FALSE, message = FALSE, results='asis'}
Assault_model_final %>% 
  tbl_regression()
```

VIF analysis

```{r, echo = FALSE, message = FALSE}
knitr::kable(t(as.data.frame(vif(Assault_model_final))), format = "html")
```

In the Assault and Battery regression, Density, Poverty, No_Diploma_Rate, and Intensity_Poverty emerged as significant variables, with Intensity_Poverty having the most substantial impact (beta of 8.235).
The VIF test confirmed the absence of multicollinearity, and the Adjusted R-Squared improved to around 0.37.

Our final formula is the following: 
$AssaultandBattery = \beta_0 + \beta_1 Density + \beta_2Poverty + \beta_3NoDiplomaRate + \\ \beta_4ImmigrationRate + \beta_5IntensityPoverty$

### Burglaries

We run the regression with Burglaries and find this reduced model

```{r, echo = FALSE, message = FALSE, results='asis'}
Burglary_model_final %>% 
  tbl_regression()
```

VIF analysis

```{r, echo = FALSE, message = FALSE}
knitr::kable(t(as.data.frame(vif(Burglary_model_final))), format = "html")
```

For the Burglaries regression, all variables remained highly significant.
Notably, Poverty and No_Diploma_Rate negatively affected predictions (-19.624/-17.833), while Unemployment had the most significant positive impact (71.162), followed by Immigration (26.937) and Intensity_Poverty (16.391).
The VIF test assured us of no multicollinearity issues, though the Adjusted R-Squared was approximately 0.19.

Our final formula is the following: $Burglary = \beta_0 + \beta_1Poverty + \beta_2NoDiplomaRate + \beta_3ImmigrationRate + \\ \beta_4UnemploymentRate + \beta_5IntensityPoverty$

### Intentional damage and destructions

We run the model with Damage and Destruction

```{r, echo = FALSE, message = FALSE, results='asis'}
Damage_model_final %>% 
  tbl_regression()
```

VIF analysis

```{r, echo = FALSE, message = FALSE}
knitr::kable(t(as.data.frame(vif(Damage_model_final))), format = "html")
```

In the Intentional Damage and Destruction regression, Poverty, Intensity_Poverty, Density, and somewhat less so Win_Lepen were highly significant.
Both Poverty and Intensity had a substantial positive impact (\~15), while the impact of Win_Lepen was negligible.
The VIF test once again confirmed no multicollinearity.

Our final formula is the following: $DamageDestruction = \beta_0 + \beta_1Poverty + \beta_2WinLepen + \beta_3IntensityPoverty + \beta_4 Density$

### Drug Use

We run the model with Drug use as our dependent variable

```{r, echo = FALSE, message = FALSE, results='asis'}
Drug_model_final %>% 
  tbl_regression()
```

VIF analysis

```{r, echo = FALSE, message = FALSE}
knitr::kable(t(as.data.frame(vif(Drug_model_final))), format = "html")
```

For the Drug Use regression, the AIC stepwise regression test retained all variables except TotalPop.
Poverty and Immigration Rate had the most significant positive impacts (7.769/6.178), while Unemployment had a considerable negative impact (-9.551).
The VIF test indicated no multicollinearity issues.

Our final formula is the following: $DrugUse = \beta_0 + \beta_1 Density + \beta_2Poverty + \beta_3NoDiplomaRate + \beta_4ImmigrationRate + \\ \beta_5UnemploymentRate + \beta_6WinLepen + \beta_7IntensityPoverty$

### Theft without violence

We run the model with Theft as our independent variable

```{r, echo = FALSE, message = FALSE, results='asis'}
Theft_model_final %>% 
  tbl_regression()
```

VIF analysis

```{r, echo = FALSE, message = FALSE}
knitr::kable(t(as.data.frame(vif(Theft_model_final))), format = "html")
```

In the Theft without Violence regression, Immigration Rate and Density were the only highly significant variables.
The positive impact of Immigration_Rate was substantial (\~20), but the low Adjusted R-Squared suggests challenges in interpreting results.
Nevertheless, the VIF test confirmed no multicollinearity issues in this regression."

Our final formula is the following: $Theft = \beta_0 + \beta_1 Density + \beta_2WinLepen + \beta_3ImmigrationRate + \\ \beta_4UnemploymentRate + \beta_5IntensityPoverty$

## Discussing our results

In our initial research, we wanted to understand if Unemployment could predict Crime in France.
When we analyzed all types of crimes together, we found a connection between Unemployment and Crime.
However, our findings lacked precision due to a low Adjusted R-Squared value.
Upon further investigation, looking at each crime type separately, we found some interesting results.
Unemployment's influence on predicting Crime appeared to change depending on the specific crime category.
For instance, in cases like *Assault and Battery* and *Intentional Damage and Destruction*, Unemployment didn't seem to significantly impact the calculations.
This was counterintuitive for our expectations.
Moreover, concerning *Burglaries* and *Theft without Violence*, Unemployment emerged as a more critical factor.
It became the primary predictor for the occurrence of these crime types.

We then delved into the potential impact of Poverty on predicting Crime in France.
We examined two datasets: one reflecting the number of people affected by poverty in each town ('Poverty_2019') and another showing how far individuals were to the poverty threshold ('Intensity_Poverty').
Again, we analyzed each crime category separately for accuracy.
In certain crimes, such as *Assault and Battery* and *Intentional Damage and Destruction*, poverty and its intensity significantly influenced crime rates.
We then faced a very surprising result when computing the regression with the *Burglaries*, in this case, Poverty seems to have an important negative impact while the Intensity of Poverty has a postive impact.
The VIF factor was also under 5 meaning that multicollinearity was not the reason for that result.
This leads us to the interpretation that when talking about Burglaries, the amount of poor people in a town would have a negative impact since Richer neighbourhoods are more likely to be burglarized.
In the case of Intensity of Poverty, this varibale is not an indicator of how many people are poor, but rather how poor they are we could assume that the poorest people who burglarize.
Regarding Drug Use crimes, Poverty emerged as a significant predictor, but with notably lesser impact compared to previous regressions.
Similarly, when examining 'Theft without Violence,' while 'Intensity_Poverty' showed promise, it didn't reach statistical significance.
In essence, while Poverty and its intensity play substantial roles in predicting criminal behavior in France, their impact varies based on the specific crime type, often leading to conflicting trends.

Moving on to the impact of immigration on crime rates in France, our analyses revealed nuanced outcomes.
For instance, in 'Assault and Battery' and 'Intentional Damage and Destruction' cases, the Immigration variable appeared insignificant, with minimal influence.
However, in Burglaries and Drug-related crimes, Immigration seemed to exert a significant effect.
Nonetheless, its impact on 'Theft without Violence' remained uncertain due to a low Adjusted R-Squared value, cautioning against definitive conclusions.
Overall, while Immigration played a significant role in some models, its impact varied considerably among different crime types.

We also explored the role of Population Density in predicting criminal activity.
Interestingly, Density didn't seem to affect Burglaries much, possibly because criminals find it easier to operate in less crowded, rural areas, For example, in the department of Gironde, where Bordeaux is located, the city with the most burglaries.
Concerning the remaining crime types, Density is always significant, but has a small coefficient.
We observe that some of the most criminal cities in France, such as Marseille or Lyon are not very dense.
This explains why Density may not be the best factor to explain Crime.

In terms of Education level, the data suggests that the population without a diploma doesn't always have the highest crime rates, which might be unexpected.
For instance, in the case of *Assault and Battery*, our findings indicate that crime rates do relate to education level, but the impact is minimal.
In many areas across France, especially in the northeastern mining regions, there's a large number of individuals with diplomas, yet the crime rates there is remarkably low.
However, in La Courneuve (93) a city in the Paris region with a notably high crime rate, there is a considerable proportion of people without a diploma.
Furthermore, the absence of a diploma seems to have a negative correlation with Burglary rates, with a significant factor of -17.
This isn't surprising as it is a wealthier region, implying that cities with a higher education level might be the primary targets for burglaries.
Regarding Drug Use, it was unexpected to see that the absence of a diploma negatively impacts the regression.
This could be explained by acknowledging that drug use is widespread among the population in France, affecting even the more educated regions.

Lastly, we explored whether there was a connection between voting patterns in the 2017 presidential election and the crime rates.
We aimed to understand if the way people voted affected the crimes committed in those areas and if political behavior correlated with observed criminality.
While the AIC eliminated our Voting variables in most of our regressions, an interesting negative relationship emerged between Marine Le Pen "winning" the city and both *Drug Use* and *Intentional Damage and Destruction* regressions.
For instance, if a city voted in majority for Marine Le Pen in 2017, it had on average an *Intentional Damage and Destruction* rate 0.362 lower than a city that voted against her.
That decrease was 0.319.
in the *Drug Use* category..
However, apart from these instances, the Le Pen variables weren't significant enough to draw conclusive remarks for our other variables.
