---
title: "What is the impact of socio-economic factors on Criminality in France?"
format: 
  revealjs:
    scrollable: true
editor: visual
---

```{r, echo = FALSE, message = FALSE, include=FALSE}
load(file = here::here("Report/Data_for_EDA.RData"))
source(here::here("Script/Regression.R"))
options(gt.summary.table.width = 0.7)

```

# Introduction

## Research questions {.smaller}

-   **Can the criminality rate in France be explained using the unemployment rate ?**

-   **Can the criminality rate in France be explained using the poverty rate ?**

-   **Can the criminality rate in France be explained using education indicators ?**

-   **Can the density of population in territories explain criminality ?**

-   **Can the immigration rate explain criminality ?**

-   **Can the previous presidential results in territories have an impact on criminality ?**

-   **Is there a correlation between these mentioned variables ?**

## Motivations

Crime is a polarizing topic, most people do not agree on what causes crime. A statistical analysis could give leads into the causes of criminality.

# Variables

We will consider the following macroeconomic variables:

-   Poverty rate

-   Unemployment rate

-   Percentage of people above 25 without a diploma

-   Density of Population

-   Results of previous presidential elections

-   Immigration

## Extreme values {.smaller}

Most of our dataset were challenging to use because there were some surprising extreme values.

Lessons from our datasets:

Paris is an outlier, proven by clustering

```{r, message=FALSE, echo=FALSE, results='asis'}
cluster_map
```

## Surprising values

Some villages "Died for France", now have population of 0.

High crime rate in:

-   Touristic destinations

-    Airports

Density varies and may be very low in some towns because of Natural Reserves.

## Maps

```{r, echo=FALSE, message=FALSE, results='asis'}
leaf_cap_map
```

## Regressions

With all types of crime:

```{r, echo = FALSE, message = FALSE, results='asis'}
x <- Full_model %>% 
  tbl_regression()
y <- Reduce_model %>% 
  tbl_regression()

tbl_merge(
  tbls = list(x, y),
  tab_spanner = c("**Full model**", "**Reduced model**")
)
```

No issues of multicollinearity (VIF<5) low Adjusted R square.
New regressions this time for each crime type.

## Assault and Battery

```{r, echo = FALSE, message = FALSE, results='asis'}
Assault_model_final %>% 
  tbl_regression()
```

## Burglaries

```{r, echo = FALSE, message = FALSE, results='asis'}
Burglary_model_final %>% 
  tbl_regression()
```

## Intentional damage and destructions

```{r, echo = FALSE, message = FALSE, results='asis'}
Damage_model_final %>% 
  tbl_regression()
```

## Drug Use

```{r, echo = FALSE, message = FALSE, results='asis'}
Drug_model_final %>% 
  tbl_regression()
```


## Theft without violence

```{r, echo = FALSE, message = FALSE, results='asis'}
Theft_model_final %>% 
  tbl_regression()
```
